\documentclass[12pt]{article}
\begin{document}
\author{Luyu Liu}

\newcounter{para}
\newcommand\para{\par\refstepcounter{para}\thepara\space}

\section*{CSE 5194 WEEK5 - HPC}
\title{CSE 5194 WEEK5 - HPC}
\section{HPC continue}

\paragraph{RSockets}
Implements various socket like functions functions:
\\ functions take smae parmeters as sockets.

\subparagraph{RDMA over converged enhanced ethernet (RoCE)}
network stack comparison

Pros: IB vs RoCE:
works natively in ethernet environments.

Not working with traditional network management tools: that's where v2 kicks Implements

\paragraph{OmniPath}
Pathcalse came upwith initial version of BI based product.

Qlogic enhanced the product with the PSM sotware interface.

The IB product of QLogic was acquired by intel.

network on loading: offloading.

OFI: Omnipath adapter: no competition.

\paragraph{conclusion}
all model support RDMA;

\paragraph{OpenFabrics}
openIB: specification, but people were not following the standard.

Verbs interface: openfabrics stack with uniied verbs interface:

User actaully has a lot of choices: user leel, kernel level, adapters.

\subparagraph{libfabrics: software stack}
OpenFabrics Interfaces (OFI) is a framework focused on exporting fabric communication services to applications. OFI is best described as a collection of libraries and applications used to export fabric services. The key components of OFI are: application interfaces, provider libraries, kernel services, daemons, and test applications.

Interconnect: IB, ethernet, Omnipath. Competing schemas.

top500.org: actually infiniband and custom have the largest performance share, meaning that some largest supercomputer are suing them.

\subparagraph{Ethernet based scientific computing installations}
Most are chinese. alibaba, baidu data center. Benchmark: high performance and submit.

\section{HPC part II}
\paragraph{Frequency and power} Exponential.

\subparagraph{Tick Tock}
Tick–tock was a production model adopted in 2007 by chip manufacturer Intel. Under this model, every microarchitecture change (tock) was followed by a die shrink of the process technology (tick). Its replacement was announced in 2016, called "Process, Architecture, Optimization", and is similar to a tick–tock cycle, followed by an optimization phase.

\paragraph{AVX technology}
History: clay. Vector machine: Advanced Vector Extensions
SIMD: Single instruction, multiple data
Advanced Vector Extensions

512 bits SIMD Extensions


\paragraph{motivation}
GPU grows way faster than CPU.

GPU hardware:

\paragraph{Supercomputing products}
Tesla C1070: server blade.

NVIDIA Volta is optimized for deep learning workloads: 
has dedicated tensor cores for both training and inference.


\subparagraph{volta nvlink}
Extra channels between each GPUS.

\paragraph{ARM}
Lowpower processors: 

\paragraph{TPU, IPU, and other architectures}
Talk later. quickly skim thru.




\end{document}