\documentclass[12pt]{article}
\begin{document}
\author{Luyu Liu}

\newcounter{para}
\newcommand\para{\par\refstepcounter{para}\thepara\space}

\section*{CSE 5194 WEEK6 - HPC}
\title{CSE 5194 WEEK6 - HPC}
\section{Trend in high-performance storage}

\paragraph{NVM}
PCIe SSDs standard. non-valatile memory express (NVMe)

expanding NVMe to fabrics.

\paragraph{Communication middleware}
parallel programming models:
\subparagraph{provide abstract machine models}
models can be mapped on different types of systems: distributed shsared moemory DSM, MPI within a node.

\paragraph{MPI}

\subparagraph{allreduce collective communication pattern}
ui
\subparagraph{GPU aware MPI liabrary MVAPICH2-GDR}

\section{Caffe - deep learning framework}
\subsection{inner working of neural networks}
$$y = w \cdot x + b$$

$$y = g(Wx + b)$$
g is the non linear transporformation: maybe we are warping the space.

\subparagraph{concepts}
$$z = g(Vg(Wx+b))$$

\subparagraph{classification using neural nework=}

$P(y|x) = sfmax(Wg(Vf(x)))$

\subparagraph{traning}
$L(x, i^*) = logP(y=i^*|x)$

\subparagraph{complexity of forwar propagation and back propagation}

\subparagraph{conclusion}

\subsection{caffe}
convolutional architecture for fast feature embedding

Alexnet;

HPilosophy behind developing Caffe:

\paragraph{expression}
models and optimizations are defined as plaintext schemas instead of code.

\paragraph{highlight}
Speration of representation and implementation:
Caffe model definitions are written as config files using the protocol buffer language

Test coverage: Every single module in  caffe is tested/

Python and matlab; pretrained model.

\paragraph{data storage}
stores using blobs;
\subsubsection{blobs}
traditionally, stored in 4D arrray.: why?

\subsubsection{protocol buffers}
level DB is a key value store builty by google: it is a file system;
doesn't provide a server or cmd.

models are stored to disk as buffers.

\subsubsection{layers and networks and run mode}
layers has to roles: I forget
bookkeeping for all directed acyclic graph of layers

\subsubsection{Solver}
SGD; ADADELTA; ADAPTIVE GRADIENT;

run: ./build.tools/caffe train foo.prototext

Take a lot of time to create originally

\end{document}